|

### 2021-03-14 supplementary_information_sciad.Rmd
edits: supp materials, minor edits

```{=tex}
\begin{equation}
  w_{ij} = w(v_i, v_j)
\end{equation}
```
The weight factor should represent the likelihood of $u$ changing from $u_i$ to $u_j$ with a common $v = v_i$ (note that $v_i$ is in general a vector of explanatory variables for data point $i$). We used the following weighting function based on Mahalanobis distances following Gelman and Pardoe [@gelmanAveragePredictiveComparisons2007]:

```{=tex}
\begin{equation}
w(v_i, v_j) = \frac{1}{1 + (v_i - v_j)^T\Omega_v^{-1}(v_i-v_j)}
\end{equation}
```
where $\Omega_v^{-1}$ is the inverse of the variance-covariance matrix of $v$. The function gives the maximum weight for a pair of $u_i$ and $u_j$ if $v_i = v_j$ ($v=v_i$ when $u = u_i$) while giving a less weight as the Mahalanobis distance between $v_i$ and $v_j$ increases. This property makes sense because our goal is to approximate the probability of transition from $u_i$ to $u_j$ with a common $v$ (i.e., $v_i = v_j$).

>>>>

```{=tex}
\begin{equation}
  w_{ij} = w(v_i, v_j)
\end{equation}
```
The weight factor should represent the likelihood of $u$ changing from $u_i$ to $u_j$ with a common $v = v_i$ ($v_i$ is in general a vector of explanatory variables for data point $i$). We used the following weighting function based on Mahalanobis distances following Gelman and Pardoe [@gelmanAveragePredictiveComparisons2007]:

```{=tex}
\begin{equation}
w(v_i, v_j) = \frac{1}{1 + (v_i - v_j)^T\Omega_v^{-1}(v_i-v_j)}
\end{equation}
```
where $\Omega_v^{-1}$ is the inverse of the variance-covariance matrix of $v$. Note that $v=v_i$ when $u = u_i$, and $v=v_j$ when $u = u_j$. The function gives the maximum weight for a pair of $u_i$ and $u_j$ if $v_i = v_j$ while giving a less weight as the Mahalanobis distance between $v_i$ and $v_j$ increases. This property makes sense because our goal is to approximate the probability of transition from $u_i$ to $u_j$ with a common $v$ (i.e., $v_i = v_j$).
